Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-14 paper/paper.tex
engine tables

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{ccr}
    \toprule
    Name & URL & \# Stars \\
    \midrule
    MS's Chakra & \cite{chakra2018repo} & 7200+ \\
    Google's v8 & \cite{v82018repo} & 9800+ \\
    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
    Mozilla's Rhino & \cite{rhino2018repo} & 1800+ \\
    JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{cccr}
    \toprule
    Group & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
    Moddable & XS & \cite{xs2018repo} & 140+ \\
    \midrule
    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}
